\documentclass[submission,copyright,creativecommons]{eptcs}
\providecommand{\event}{SYNT 2018} % Name of the event you are submitting to
\usepackage{breakurl}             % Not needed if you use pdflatex only.
\usepackage{underscore}           % Only needed if you use pdflatex.

\usepackage{booktabs} % For formal tables
\usepackage{amsmath}%
\usepackage{amssymb}
\usepackage{wasysym}%
\usepackage{cleveref}
\usepackage{graphicx}
\usepackage{chngpage}
\usepackage{subcaption}
\usepackage{xcolor}

\title{Warm-Starting Fixed-Point Based Control Synthesis}
\author{Zexiang Liu \qquad\qquad Necmiye Ozay
\institute{EECS\\
University of Michigan\\
Ann Arbor, United States}
\email{zexiang@umich.edu \quad\qquad necmiye@umich.edu}
\and
Nicolas Perrin
\institute{CNRS UMR 7222, ISIR \\
	Sorbonne Universit\'{e} \\
Paris, France}
\email{\quad perrin@isir.upmc.fr  }
}
\def\titlerunning{Warm-Starting Fixed-Point Based Control Synthesis}
\def\authorrunning{Z. Liu, N. Ozay \& N. Perrin}

\newtheorem{example}{Example}
%\newtheorem{proof}{Proof}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}
\newtheorem{assumption}{Assumption}
\newtheorem{problem}{Problem}
\newtheorem{theorem}{Theorem}

\newcommand*{\QEDB}{\hfill\ensuremath{{\blacksquare}}}%

\begin{document}
\maketitle

\begin{abstract}
In this work we propose a patching algorithm to incrementally modify controllers, synthesized to satisfy a temporal logic formula, when some of the control actions become unavailable. The main idea of the proposed algorithm is to ``warm-start" the synthesis process with an existing fixed-point based controller that has a larger action set. 
By exploiting the structure of the fixed-point based controllers, our algorithm avoids repeated computations while synthesizing a controller with restricted action set. Moreover, we show that the algorithm is sound and complete, that is, it provides the same guarantees as synthesizing a controller from scratch with the new action set.    
An example on synthesizing controllers for a hopping {\color{purple} walking} robot under ground constraints is used to illustrate the approach. In this application, the ground constraints determine the action set and they might not be known a priori. Therefore it is of interest to quickly modify a controller synthesized for an unconstrained surface, when new constraints are encountered. Our simulations indicate that the proposed approach provides at least an order of magnitude speed-up compared to synthesizing a controller from scratch.
\end{abstract}

\input{warmstart-body}

%\nocite{*}
\bibliographystyle{eptcs}
\bibliography{warmstart}

\appendix
\input{appendix}

\end{document}
