\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables
\usepackage{amsmath}%
%\usepackage{MnSymbol}%
\usepackage{wasysym}%
\usepackage{cleveref}
\usepackage{graphicx}
%\usepackage{longtable}
\usepackage{chngpage}
\usepackage{subcaption}
\usepackage{color}
%\usepackage{mathrsfs}


% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
%\acmDOI{10.475/123_4}

% ISBN
%\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[EMSOFT'18]{International Conference on Embedded Software}{September 2018}{Torino, Italy}
\acmYear{2018}
%\copyrightyear{2016}


%\acmArticle{4}
%\acmPrice{15.00}

% These commands are optional
%\acmBooktitle{Transactions of the ACM Woodstock conference}
%\editor{Jennifer B. Sartor}
%\editor{Theo D'Hondt}
%\editor{Wolfgang De Meuter}
\newtheorem{remark}{Remark}
\newtheorem{assumption}{Assumption}
\newtheorem{problem}{Problem}

\begin{document}
\title{Warm-Starting Fixed-Point Based Control Synthesis}
%\titlenote{Produces the permission block, and
%  copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
% \texttt{acmart.pdf} document}


\author{Anonymous Submission}

% The default list of authors is too long for headers.
\renewcommand{\shortauthors}{Anonymous et al.}


\begin{abstract}
 In this work we propose a patching algorithm to incrementally modify controllers, synthesized to satisfy a temporal logic formula, when some of the control actions become unavailable. The main idea of the proposed algorithm is to ``warm-start" the synthesis process with an existing fixed-point based controller that has a larger action set. 
By exploiting the structure of the fixed-point based controllers, our algorithm avoids repeated computations while synthesizing a controller with restricted action set. Moreover, we show that the algorithm is sound and complete, that is, it provides the same guarantees as synthesizing a controller from scratch with the new action set.    
An example on synthesizing controllers for a hopping robot under ground constraints is used to illustrate the approach. In this application, the ground constraints determine the action set and they might not be known a priori. Therefore it is of interest to quickly modify a controller synthesized for an unconstrained surface, when new constraints are encountered. Our simulations indicate that the proposed approach provides at least an order of magnitude speed-up compared to synthesizing a controller from scratch.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10010520.10010553.10010554.10010556</concept_id>
<concept_desc>Computer systems organization~Robotic control</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}


\ccsdesc[500]{Computer systems organization~Robotic control}	


\keywords{control synthesis, formal method, warm-start, fixed-point}


\maketitle

\input{warmstart-body}


\bibliographystyle{ACM-Reference-Format}
\bibliography{warmstart}

\appendix
\input{appendix}

\end{document}
